\documentclass[11pt,a4paper]{article}
\usepackage{geometry}
\usepackage{hyperref}
\usepackage{mathpazo}
\usepackage[scaled=0.92]{helvet}
\usepackage{courier}
\usepackage{amssymb}
\usepackage{enumitem}
\geometry{top=0.3in, bottom=0.3in, left=0.3in, right=0.3in}
\hypersetup{colorlinks=true, linkcolor=black, urlcolor=blue}
\linespread{0.8}
\begin{document}
\begin{center}
\fontsize{22}{22}\textbf{SALAH-ELDIN HASSEN}\\[0.2cm]
\fontsize{11}{12}\textbf{ (+20) 1127709232 \texttt{|} Giza / Egypt \texttt{|}  \href{mailto:salah0eldin.work@gmail.com}{salah0eldin.work@gmail.com} \texttt{{|}} \href{https://www.linkedin.com/in/salah-eldin-hassen-5bba10250/}{LinkedIn Profile} \texttt{{|}} \href{https://github.com/salah0eldin}{Github Profile}}\\[-0.1cm]
\rule{\textwidth}{0.3pt}\\
\end{center}
\vspace{-0.9cm}
\begin{center}
\section*{\fontsize{14}{18}\textbf\selectfont EDUCATION}
\end{center}
\vspace{-0.2cm}
\renewcommand\labelitemi{\raisebox{0.2ex}{\scriptsize$\bullet$}}
\begin{flushleft}
\textbf{Cairo University Faculty of Engineering (CUFE)}\hfill\textit{2021 - 2026}\\
\end{flushleft}
\vspace{-0.6cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} Bachelor of Electronics and Communications (EECE) With Cumulative Grade: (Very Good).
\end{itemize}
\vspace{-0.3cm}
\vspace{-0.2cm}
\rule{\textwidth}{0.3pt}\\
\vspace{-0.9cm}
\begin{center}
\section*{\fontsize{14}{ 18 }\textbf\selectfont WORK EXPERIENCE}
\end{center}
\vspace{-0.2cm}
\begin{flushleft}
\textbf{Autonomous Embedded Member \texttt{|} Cairo University Eco Racing Team \texttt{|} Part-time}\hfill\textit{Apr 2025 - Current}\\
\end{flushleft}
\vspace{-0.6cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} Mainly debugging and handling CAN protocol, GPS Module and motor driver.
\end{itemize}
\vspace{-0.5cm}
\begin{flushleft}
\textbf{Robotics \& Embedded Instructor \texttt{|} Beta Academy \texttt{|} Seasonal}\hfill\textit{Jan 2023 - Jan 2025}\\
\end{flushleft}
\vspace{-0.6cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} Taught Programming and Arduino to over 600 students with consistently excellent feedback.
\end{itemize}
\vspace{-0.5cm}
\begin{flushleft}
\textbf{Coding AI Trainer \texttt{|} Outlier \texttt{|} Freelancing}\hfill\textit{Sep 2024 - Dec 2024}\\
\end{flushleft}
\vspace{-0.6cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} Trained and optimized AI models for coding in C++ and Python tasks to enhance code generation accuracy.
\end{itemize}
\vspace{-0.5cm}
\vspace{0.2cm}
\rule{\textwidth}{0.3pt}\\
\vspace{-0.9cm}
\begin{center}
\section*{\fontsize{14}{18}\textbf\selectfont SKILLS}
\end{center}
\vspace{-0.4cm}
\renewcommand{\arraystretch}{1.8} % Adjust row spacing
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}} l l}
\textbf{Digital:} & HDL languages (VHDL, Verilog, System Verilog) - TCL - FPGA Xilinx - Linting. \\ 
\textbf{Software:} & C/C++ - Python - MATLAB - OOP - Automation - Scripting - AI tools - Qt - Git \& GitHub - LaTeX. \\ 
\textbf{Embedded:} & STM32 - ARM Cortex-M - AVR - PIC - FreeRTOS - I2C - USART - SPI - CAN - SOMEIP. \\ 
\textbf{OS:} & Linux (Fedora(main), Kali Nethunter, Ubuntu) - Windows. \\ 
\end{tabular*}
\vspace{0.2cm}\rule{\textwidth}{0.3pt}
\vspace{-0.5cm}
\centering
\section*{\fontsize{14}{18}\textbf\selectfont PROJECTS}
\vspace{-0.3cm}
\begin{flushleft}
\textbf{SPI Slave Interface}\texttt{|} {\href{https://github.com/salah0eldin/Digital-Projects/tree/master/SPI_Slave_Interface}{Link}}\hfill\textit{Spring 2025}\\
\end{flushleft}
\vspace{-0.6cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} Designed a modular SPI Slave Interface with RAM modules and validated using self-checking testbenches.
\item \setlength{\itemsep}{-0.0em} Vivado - Questasim - Verilog - SPI - Single-Port RAM - Constraints - Linting.
\end{itemize}
\vspace{-0.3cm}
\begin{flushleft}
\textbf{Spartan-6 DSP48A1}\texttt{|} {\href{https://github.com/salah0eldin/Digital-Projects/tree/master/DSP48A1}{Link}}\hfill\textit{Spring 2025}\\
\end{flushleft}
\vspace{-0.6cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} Designed and tested a DSP48A1 block in Verilog with C++ golden model and Verilog test benches.
\item \setlength{\itemsep}{-0.0em} Verilog - DSP48A1 - C++ Simulation - Test Benches - Linting.
\end{itemize}
\vspace{-0.3cm}
\begin{flushleft}
\textbf{FreeRTOS-Based Dual Microcontroller Door Security System}\texttt{|} {\href{https://www.linkedin.com/feed/update/urn:li:activity:7261751302018244608/}{Link}}\hfill\textit{Summer 2024}\\
\end{flushleft}
\vspace{-0.6cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} Implemented password authentication, EEPROM storage via I2C, and automated door control mechanisms.
\item \setlength{\itemsep}{-0.0em} ATMega32 - I2C - USART - EEPROM - FreeRTOS.
\end{itemize}
\vspace{-0.3cm}
\begin{flushleft}
\textbf{Simulation \& Linting Scripts}\texttt{|} {\href{https://github.com/salah0eldin/Scripts}{Link}}\hfill\textit{Winter 2024}\\
\end{flushleft}
\vspace{-0.6cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} Developed Python and Shell scripts for creating do files, running ModelSim, waveform viewing (GTKWave).
\item \setlength{\itemsep}{-0.0em} Created Python script that creates TCL files for linting designs using Qverify.
\item \setlength{\itemsep}{-0.0em} Python - Shell - TCL - GTKWave - Qverify.
\end{itemize}
\vspace{-0.3cm}
\begin{flushleft}
\textbf{Advanced Tic Tac Toe Game}\texttt{|} {\href{https://www.linkedin.com/posts/salah-eldin-hassen-5bba10250_qt-cplusplus-softwaredevelopment-activity-7227345922031009793-xhzd/?rcm=ACoAAD4WDF8Bk9P5oS-irdrlv53Rzjd03ps4OSA}{Link}}\hfill\textit{Spring 2024}\\
\end{flushleft}
\vspace{-0.6cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} Created the game with AI (minimax), user authentication, game history, and a Qt-based GUI.
\item \setlength{\itemsep}{-0.0em} Automated testing via Qt Test and GitHub Actions.
\item \setlength{\itemsep}{-0.0em} C++ - Minimax Algorithm - Secure Hashing - Qt - Qt Test - SQLite - Git - GitHub Actions.
\end{itemize}
\vspace{-0.3cm}
\begin{flushleft}
\textbf{Multi-CV Generator Script}\texttt{|} {\href{https://github.com/salah0eldin/CV}{Link}}\hfill\textit{Spring 2025}\\
\end{flushleft}
\vspace{-0.6cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} Developed a Python script to generate ATS-friendly LaTeX CVs from JSON data (used to generate this CV).
\item \setlength{\itemsep}{-0.0em} Python - LaTeX - JSON.
\end{itemize}
\vspace{-0.3cm}
\begin{flushleft}
\textbf{Concurrent Rust TCP Server}\texttt{|} {\href{https://github.com/salah0eldin/RustTCPServer}{Link}}\hfill\textit{Winter 2024}\\
\end{flushleft}
\vspace{-0.6cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} Developed a multithreaded Rust TCP server, resolving port conflicts and optimizing client handling.
\item \setlength{\itemsep}{-0.0em} Rust - Multithreading.
\end{itemize}
\vspace{-0.3cm}
\vspace{-0.2cm}
\rule{\textwidth}{0.3pt}\\
\newpage
\vspace{-0.5cm}
\centering
\section*{\fontsize{14}{18}\textbf\selectfont OTHER PROJECTS}
\vspace{-0.3cm}
\begin{itemize}[noitemsep, left=0pt, itemsep=5pt]
\item Analog IC Design Projects on Cadence (Virtuoso) \texttt{|} \href{https://github.com/salah0eldin/Analog_Projects}{Link}
\item MATLAB Signal Processing and Simulink Control System Projects
\item Reverse Tic Tac Toe Game 3x3 and 4x4 using web \texttt{|} \href{https://github.com/salah0eldin/Tic_tac_toe_AVOID_THE_X}{Link} \texttt{|} \href{https://salah0eldin.github.io/Tic_tac_toe_AVOID_THE_X/}{Game}
\item Self Driving Robots - Path Planning \& Obstacle Avoidance (MATLAB, FMM2, A*) \texttt{|} \href{https://github.com/salah0eldin/PathPLanningUsingFMM2andAStar}{Link}
\item Maze-Solving Line-Follower Robot Car - Arduino-based pathfinding robot \texttt{|} \href{https://github.com/salah0eldin/ArduinoCarLineFollowerMazeSolver-Saver}{Link}
\item SFML Chess Game - C++ chess game with an interactive GUI \texttt{|} \href{https://github.com/salah0eldin/CHESS_CPP_SFML}{Link}
\item Advanced Digital Multimeter on PCB\texttt{|} {\href{https://www.linkedin.com/feed/update/urn:li:activity:7227981461818138624/}{Link}}
\item I2C-Integrated Control Unit\texttt{|} {\href{https://www.linkedin.com/feed/update/urn:li:activity:7243602012020330497/}{Link}}
\item Advanced Image Editor with Qt and OpenCV\texttt{|} {\href{https://github.com/salah0eldin/CODSOFT/tree/main/C%2B%2B/Task5%20-%20ImageProcessing/ImageEdit}{Link}}
\item Laravel Workshops System\texttt{|} {\href{https://github.com/salah0eldin/WorkshopsSystem}{Link}}
\end{itemize}
\vspace{-0.6cm}
\rule{\textwidth}{0.3pt}\\
\vspace{-0.5cm}
\centering
\section*{\fontsize{14}{18}\textbf\selectfont COURSES}
\vspace{-0.3cm}
\begin{flushleft}
\textbf{Digital Design Diploma \texttt{|} Eng: Kareem Waseem}\hfill\textit{Jan 2025 - Mar 2025}\\
\end{flushleft}
\vspace{-0.7cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} Studied digital and RTL design using Verilog for synthesis and simulation, FPGA design flow, and static timing analysis (STA).
\item \setlength{\itemsep}{-0.0em} Worked with Vivado, IP catalog, clock domain crossing, low-power design, and Questa Lint for verification.
\end{itemize}
\vspace{-0.5cm}
\begin{flushleft}
\textbf{Digital Verification Course \texttt{|} IEEE CUSB}\hfill\textit{Mar 2025 - Current}\\
\end{flushleft}
\vspace{-0.7cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} Studied formal verification, UVM, sequences, configuration, and SystemVerilog assertions.
\item \setlength{\itemsep}{-0.0em} Used QuestaSim for simulation, verification planning, and functional coverage.
\end{itemize}
\vspace{-0.5cm}
\begin{flushleft}
\textbf{Advanced Embedded Diploma \texttt{|} Eng: Ahmed Abdel-Gafar}\hfill\textit{Dec 2024 - Current}\\
\end{flushleft}
\vspace{-0.7cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} ARM Cortex-M4 architecture, debugging, memory systems, and the compilation process.
\item \setlength{\itemsep}{-0.0em} Linker script, startup code, and device driver development for GPIO, RCC, SysTick Timer, and NVIC.
\item \setlength{\itemsep}{-0.0em} Flash Memory Interface, bootloader design, implementation, and testing.
\item \setlength{\itemsep}{-0.0em} LIN and CAN communication protocols, AUTOSAR architecture, and MISRA C compliance.
\end{itemize}
\vspace{-0.5cm}
\begin{flushleft}
\textbf{Linux Fundamentals \texttt{|} IEEE ASU}\hfill\textit{Aug 2024 - Sep 2024}\\
\end{flushleft}
\vspace{-0.7cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} Learned Linux file management, shell scripting, and user permissions.
\item \setlength{\itemsep}{-0.0em} Gained skills in process control, package handling, and SSH.
\end{itemize}
\vspace{-0.5cm}
\begin{flushleft}
\textbf{SOME/IP Workshop \texttt{|} BULLET - Eng/Hazem}\hfill\textit{Oct 2024}\\
\end{flushleft}
\vspace{-0.7cm}
\begin{itemize}
\item \setlength{\itemsep}{-0.0em} Practical SOME/IP protocol workshop with client-server communication for automotive/IoT.
\end{itemize}
\vspace{-0.5cm}
\vspace{-0.1cm}
\rule{\textwidth}{0.3pt}\\
\vspace{-0.5cm}
\centering
\section*{\fontsize{14}{18}\textbf\selectfont EXTRACURRICULAR ACTIVITY}
\vspace{-0.3cm}
\begin{itemize}[noitemsep, left=0pt, itemsep=5pt]
\item First place in Robotics Competition (2022).
\item ECPC Contestant (2022, 2023).
\item NASA Hackathon participant.
\end{itemize}
\vspace{-0.6cm}
\end{document}
